---
title: "Redis for dummies"
output: html_notebook
---

Along this notebook we will explore the usage of redis. For that, a redis instance need to be running.

```{r}
system("docker run --name some-redis -p 6379:6379 -d redis")
```
Nice! Now we will need an R library to communicate with it.

```{r}
library(rredis)
```

And then do the connection.

```{r}
redisConnect(host = 'localhost')
```

Done, easy-peasy! Now we can check if a given key exists, for example.

```{r}
redisExists('foo')
```

Set it if not.

```{r}
redisSet('foo', 10)
```
```{r}
redisExists('foo')
```
And retrieve stored object.

```{r}
redisGet('foo')
```

Set it again.

```{r}
redisSet('foo', runif(10))
```
```{r}
redisGet('foo')
```
And finally, erase it when it is no longer used.

```{r}
redisDelete('foo')
```

That doesn't mean we can not set it again. Even using a set of keys to assign values.

```{r}
redisMSet(list(x=pi,y='Cazart',z=runif(2)))
# Retrieve a set of keys
redisMGet(list('z','y'))
```

```{r}
redisGet('x')
```
Even scan the whole thing.

```{r}
l <- redisKeys()
redisMGet(l)
```
Or erase the whole database.

```{r}
redisFlushAll()
redisClose()
system("docker stop some-redis")
system("docker rm some-redis")
```

